\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[colorinlistoftodos]{todonotes}
\pagestyle{empty}

\title{Word ladders report}
\author{Author 1 and Author 2}

\begin{document}
  \maketitle

  \section{Results}

  \todo[inline]{Briefly comment the results, did the script say all your solutions were correct? Approximately how long time does it take for the program to run on the largest input? What takes the majority of the time?}
  Yes all solutions correct.
  Total time for the program:

  5large1.in:
  Reading took: 0.154 seconds
  Constructing neighbours took: 2.938 seconds
  Algorithm took 5.214 seconds
  Total: 8.306 seconds

  6large2.in:
  Reading took: 0.209 seconds
  Constructing neighbours took: 1.943 seconds
  Algorithm took 0.069 seconds
  Total: 2.221 seconds

  Majority of the time is constructing neighbours and find shortest path algoritm.

  \section{Implementation details}

  \todo[inline]{How did you implement the solution? Which data structures were used? Which modifications to these data structures were used? What is the overall running time? Why?}

    Node[] words = array with all the words
    Node[] query = array with all the queries
    Map<String, List<Node>> neighbours = each word as key and its list of neighbours as value.

    Queue <Node> q = The queue which the all the nodes are put in. As the algorithm searches for a path the nodes are polled.
    Set<Node> visited = all the visited nodes will be put here
    Find Shortest Path Algorithm:
    - As long as q is not empty poll q and get the nodes neighbours. If neighbours are not visited add them to q.
    - If ending node is found return path length
    - Else return -1

    Overall running time depends on if there are a lot of neighbours or not.
    Total execution time for 5large1 was 8.3 seconds whereas 6large2 took 2.2 seconds.

\end{document}
